\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2021-03-21 paper.tex
Add stopping criterion in ISTA
algo 2 update ongoing

\begin{algorithm}[H]
\DontPrintSemicolon
\caption{Construction of the samples in $S_i^{(w)}$}
\label{alg:construct-set-S}
\KwInput{$S_i^{(w)} = \varnothing$}
\KwOutput{$S_i^{(w)}$ filled with $2N$ samples}
Compute $C_i^{(w)} \in \R^{r \times r}$ such that 
$C_i^{(w)}{C_i^{(w)}}^\top = \text{M}_i$ \tcp{Cholesky decomposition} \nonumber
\For{$\breve{n} = 1,\ldots,N$}    
{ 
  Sample $\Omega_{\breve{n}} \sim \cN(0, I_r)$ \\
  Compute $\breve{b}_{\breve{n}} = C_i^{(w)} \Omega_{\breve{n}} \in \R^r$ \\
  Update $S_i^{(w)} \leftarrow S_i^{(w)} \cup \{\breve{b}_{\breve{n}}, -\breve{b}_{\breve{n}} \}$
}
\textbf{Return:} {$S_i^{(w)}$}
\end{algorithm}

@@

$\text{M}_i= W_i$ or $\text{M}_i= D^{(w)}$

>>>>

\begin{algorithm}[H]
\DontPrintSemicolon
\caption{Construction of the samples in $S_i^{(w)}$}
\label{alg:construct-set-S}
\KwInput{$S_i^{(w)} = \varnothing$}
\KwOutput{$S_i^{(w)}$ filled with $2N$ samples}
Compute $C_i^{(w)} \in \R^{r \times r}$ such that 
$C_i^{(w)}{C_i^{(w)}}^\top = \text{M}_i^1$ \tcp{Cholesky decomposition} \nonumber
\For{$\breve{n} = 1,\ldots,N$}    
{ 
  Sample $\Omega_{\breve{n}} \sim \cN(0, I_r)$ \\
  Compute $\breve{b}_{\breve{n}}^\pm = \text{M}_{ik}^2 \pm C_i^{(w)} \Omega_{\breve{n}} \in \R^r$ \\
  Update $S_i^{(w)} \leftarrow S_i^{(w)} \cup \{\breve{b}_{\breve{n}}^+, \breve{b}_{\breve{n}}^- \}$
}
\textbf{Return:} {$S_i^{(w)}$}
\end{algorithm}

@@

$\text{M}_i^1 = W_i$ $\text{M}_{ik}^2 = W_iV_i^T\Sigma_i^{-1}(y_i - U_i\beta_k)$ or $\text{M}_i^1 = D^{(w)}$ $\text{M}_{ik}^2 = 0$
